### 2023-10-28 design/activation.tex
Fixed cafouillage

Note that the actual output of the circuit in \cref{circt:af} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the

>>>>

Note that the actual output of the circuit in \cref{circt:af} is inverted arround $V_{cm}$ a circuit such as the one shown in \cref{apsec:sumInv} inverts the the signal to its intended values.
